The pollination trade-off

### 2018-03-01 publication/supp_info.Rmd
adapt to new best random effect

```{r fig-random-intercepts, fig.height= 3, fig.cap = "Random effect intercepts"}
loadd(tidied_fixed, sites)

tidied_fixed %>%
  separate("level", c("plant_name", "site_name"), sep = "\\.", remove = F) %>%
  filter(term == "(Intercept)" ,
         var_trans == 'log',
         scale == "community", 
         pollen_category == 'heterospecific'
         ) %>%
  humanize(sites) %>%
  ggplot(aes(x = estimate, colour = plant_name, group = level)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  geom_freqpoly(size = 0.25) +
  facet_grid(locality_name + fragment ~ land_use) +
  pub_theme() +
  theme(legend.position = 'none')
```

>>>>

```{r fig-random-intercepts, eval = F, fig.height= 3, fig.cap = "Random effect intercepts"}
loadd(tidied_fixed, sites)

tidied_fixed %>%
  separate("level", c("site_name", "plant_name"), sep = "/", remove = F) %>%
  filter(term == "(Intercept)" ,
         var_trans == 'log',
         scale == "community", 
         pollen_category == 'heterospecific'
         ) %>%
  humanize(sites) %>%
  ggplot(aes(x = estimate, colour = plant_name, group = level)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  geom_freqpoly(size = 0.25) +
  facet_grid(locality_name + fragment ~ land_use) +
  pub_theme() +
  theme(legend.position = 'none')
```
